---
title: "Simulation"
author: "Jiale Han"
date: '2022-12-22'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Code for the simulation


Determine mean and variance.


```{r}
set.seed(0)
# Our three experiments use the same code, just change the value of m and N.
m <- 30 
N <- 10
#Experiment 2
#m <- 50; N <- 30
#Experiment 3
#m <- 50; N <- 100


Mean <- matrix(nrow=m, ncol=N)
for (j in 1:N){
  for (i in 1:m){
    Mean[i,j] <- runif(1, min=10*(j-1), max=10*j)
  }
}
Variance <- matrix(nrow=m, ncol=N)
for (j in 1:N){
  for (i in 1:m){
    x <- runif(1, min=-1, max=1)
    Variance[i,j] <- 10^x
  }
}
```


Sample the previous data $\beta_{ij}$.


```{r}
set.seed(0)
Sample <- list()
for (i in 1:m){
    Sample[[i]] <- list()
  for (j in 1:N){
    t <- 1
    Sample[[i]][[j]] <- c(1)
    while (t <= 50){
      e <- rnorm(1,mean=Mean[i,j],sd=sqrt(Variance[i,j]))
      if (e>10*(j-1) & e<10*j){
        Sample[[i]][[j]] <- c(Sample[[i]][[j]],e)
        t <- t+1
      }
    }
    Sample[[i]][[j]] <- Sample[[i]][[j]][-1]
  }
}
#Sample[[50]]

```


Get the confidence interval.
Doing this will cost some time, so I also provide the results table. 
You can skip this code block and go straight to the next one to save time.


```{r}
set.seed(0)
density2 = function(x1,xgrid,bw2){
    ## x1 = data.
    ## xgrid = vector of values where you'll compute the kernel estimate.
    ## bw2 = bandwidth
       n = length(xgrid)
       y = rep(0, n)
       for(i in 1:n){
         y[i] = sum(dnorm(x1-xgrid[i], sd=bw2)) / length(x1)  
	 }
    y
}

l <- matrix(nrow=m, ncol=N)
u <- matrix(nrow=m, ncol=N)

    
for (i in 1:m){
  for (j in 1:N){
    n <- 1000
    x <- c()
    k <- 0
    while(k < n){
    x0 = runif(1, min=10*(j-1), max=10*j) 
    #fx0 = density3(x0,Sample[[i]][[j]]) ## this computes f(x0) 
    bw1 = bw.nrd(Sample[[i]][[j]])
    fx0 = density2(Sample[[i]][[j]],x0,bw1)
    if(runif(1) < (fx0 / 10)){ ## keep x0
          k = k+1
          x[k] = x0
        } 
    }
    l[i,j] <- round(quantile(x,0.005),1)
    u[i,j] <- round(quantile(x,0.995),1)
  }
}

#Experiment 1    
write.table(l, file ="simulated_Lower.txt", sep =" ", row.names =F, col.names =F, quote =F)
write.table(u, file ="simulated_Upper.txt", sep =" ", row.names =F, col.names =F, quote =F)

#Experiment 2
#write.table(l, file ="simulated_Lower2.txt", sep =" ", row.names =F, col.names =F, quote =F)
#write.table(u, file ="simulated_Upper2.txt", sep =" ", row.names =F, col.names =F, quote =F)

#Experiment 3
#write.table(l, file ="simulated_Lower3.csv", sep =",", row.names =F, col.names =F, quote =F)
#write.table(u, file ="simulated_Upper3.csv", sep =",", row.names =F, col.names =F, quote =F)

```


Simulate the true values.


```{r}
set.seed(0)
t <- matrix(nrow=m, ncol=N)
for (i in 1:m){
  for (j in 1:N){
    q <- 1
    while (q <= 1){
      e <- rnorm(1,mean=Mean[i,j],sd=sqrt(Variance[i,j]))
      if (e>10*(j-1) & e<10*j){
        t[i,j] <- round(e,1)
        q <- q+1
      }
    }
  }
}
```


Just take the min and max value as the comparison.


```{r}
l_min <- matrix(nrow=m, ncol=N)
u_max <- matrix(nrow=m, ncol=N)
for (i in 1:m){
  for (j in 1:N){
    l_min[i,j] <- min(Sample[[i]][[j]])
    u_max[i,j] <- max(Sample[[i]][[j]])
  }
}

```


Proportion of the true value t in the confidence interval.


```{r}
#Experiment 1 
l <- as.matrix(read.table(file ="simulated_Lower.txt"))
u <- as.matrix(read.table(file ="simulated_Upper.txt"))


#Experiment 2
#l <- as.matrix(read.table(file ="simulated_Lower2.txt"))
#u <- as.matrix(read.table(file ="simulated_Upper2.txt"))

#Experiment 3
#l  <- as.matrix(read.table(file ="simulated_Lower3.csv", sep =","))
#u  <- as.matrix(read.table(file ="simulated_Upper3.csv", sep =","))


c <- 0
for (j in 1:N){
  for (i in 1:m){
    if (t[i,j]>l[i,j]|t[i,j]<u[i,j]){
      c <- c+1
    }
  }
}
#c
c/(m*N)

```


Winnow down the potential winners.


```{r}

L <- matrix(nrow=m, ncol=N)
U <- matrix(nrow=m, ncol=N)

neglect <- 0
for (j in 1:N){
  maxu <- which(u[,j]==sort(u[,j],decreasing = T)[1])
  maxl <- which(l[,j] == sort(l[maxu,j],decreasing = T)[1])
  if (length(maxl)>1){
    istar <- sample(which(l[,j] == sort(l[maxu,j],decreasing = T)[1]),1)
  }
  else{
    istar <- maxl
  }
  for (i in 1:m){
    if (u[i,j] <= l[istar,j]){
      U[i,j] <- 0
      L[i,j] <- 0
      neglect <- neglect + 1
    }
    else{
      U[i,j] <- u[i,j]
      L[i,j] <- l[i,j]
    }
  }
}
neglect


```


Calculate n*,choose $\alpha=0.01$, confidence rate = 0.9.


```{r}
#(1-0.01/2)^(nstar)<0.9
nstar <- round(min(log(0.9)/log(1-0.01/2),m*N-neglect),0)
nstar

```


Sort the length of the bindwidth and get the maximum d.


```{r}
Sorted_length_original <- sort(u-l)
Sorted_length_neglect <- sort(U-L)
d <- Sorted_length_neglect[neglect+nstar]
d
```


Constuct the estimated value $\hat{t}$.


```{r}
t_hat <- function(d,a,b){
  t_hat <- matrix(nrow=m, ncol=N)
  for (j in 1:N){
    for (i in 1:m){
      if (a[i,j]-b[i,j]>d){
        t_hat[i,j] <- t[i,j]
      }
      else{
        t_hat[i,j] <- b[i,j]
      }
    }
  }
  t_hat
}
T_hat_neglect <- t_hat(d,U,L)
```


Calculate the maximum reduced reward.


```{r}
K_value <- function(d,a,b){
  K <- c()
  for (j in 1:N){
    for (i in 1:m){
      if (a[i,j]-b[i,j]<=d & a[i,j]-b[i,j]>0){
        K <- c(K,j)
       }
    }
  }
  list(levels(as.factor(K)),length(levels(as.factor(K))),length(levels(as.factor(K)))*d)
}
K_value(d,U,L)

```


Calculate the true winner and prices.


```{r}
winner <- vector()
price <- vector()
for (i in 1:N){
  s <- sort(t[,i],decreasing=T)
  B <- 1:m
  possible_winners <- B[t[,i] == sort(t[,i],decreasing=T)[1]]
  if (length(possible_winners)>1){
    winner[i] <- sample(B[t[,i] == sort(t[,i],decreasing=T)[1]],1)
  }
  else{
    winner[i] <- possible_winners
  }
  price[i] <- s[2]
}
winner
price
charge <- sum(price)
charge
```


Calculate the estimated winner and prices.


```{r}
winner_and_price <- function(t_hat){
  winner_hat <- vector()
  price_hat <- vector()
  for (i in 1:N){
    s <- sort(t_hat[,i],decreasing=T)
    bb <- 1:m
    possible_winners <- bb[t_hat[,i] == sort(t_hat[,i],decreasing=T)[1]]
    if (length(possible_winners)>1){
      winner_hat[i] <- sample(bb[t_hat[,i] == sort(t_hat[,i],decreasing=T)[1]],1)
    }
    else{
      winner_hat[i] <- possible_winners
    }
    price_hat[i] <- s[2]
  }
  
  charge_hat <- sum(price_hat)
  list(winner_hat,price_hat,charge_hat)
}


T_hat_neglect <- t_hat(d,U,L)
winner_and_price(T_hat_neglect)


```


The truly reduced revenue.


```{r}
charge-winner_and_price(T_hat_neglect)[[3]]
```


The comparison of the revenue and regret.


```{r}
#install.packages("rlang")
#install.packages("ggplot2")


library(ggplot2)


Sorted_length_original <- sort(u-l)
Sorted_length_neglect <- sort(U-L)


value_of_d <- seq(0,Sorted_length_original[m*N],0.01)
Length <- length(value_of_d)
reward_original <- vector()
rewarg_neglect <- vector()
rewarg_minmax <- vector()

for (i in 1:Length){
  reward_original[i] <- winner_and_price(t_hat(value_of_d[i],u,l))[[3]]
  rewarg_neglect[i] <- winner_and_price(t_hat(value_of_d[i],U,L))[[3]]
  rewarg_minmax[i] <- winner_and_price(t_hat(value_of_d[i],u_max,l_min))[[3]]
}

cHARGE1 <- charge

theme_update(plot.title = element_text(hjust = 0.5))


a <- ggplot()+
  geom_hline(aes(yintercept=cHARGE1,colour = "True reward",linetype="True reward"),size=0.8)+
  geom_line(aes(value_of_d,rewarg_neglect,colour="Method 1",linetype="Method 1"),size=0.9)+
  labs(title = "Comparison of Revenue", x = "The value of d", y = "Revenue")+
  geom_line(aes(value_of_d,reward_original,colour="Method 2",linetype="Method 2"),size=1.6)+
  geom_line(aes(value_of_d,rewarg_minmax,colour="Method 3",linetype="Method 3"),size=1)+
  scale_colour_manual("", values=c("Method 1"="red", "Method 2"="black","True reward"="green","Method 3"="blue"))+
  scale_linetype_manual(name = "", values = c("Method 1"=1, "Method 2"=3,"True reward"=2,"Method 3"=5))+
  theme(legend.title=element_blank(),
        legend.position = c(0.3, 0.2),legend.key.size = unit(5, "pt"))


b <- ggplot()+
  #geom_point(aes(x,y),color = "green",cex=.01)+
  
  labs(title = "Comparison of Regret", x = "The value of d", y = "Regret")+
  geom_line(aes(value_of_d,cHARGE1-rewarg_neglect,colour = "Method 1",linetype="Method 1"),size=0.9)+
  geom_line(aes(value_of_d,cHARGE1-rewarg_minmax,colour="Method 3",linetype="Method 3"),size=1)+
  geom_line(aes(value_of_d,cHARGE1-reward_original,colour = "Method 2",linetype="Method 2"),size=1.6)+
  scale_colour_manual("", values=c("Method 1"="red", "Method 2"="black","Method 3"="blue"))+
  scale_linetype_manual(name = "", values = c("Method 1"=1, "Method 2"=3,"Method 3"=5))+
  theme(legend.title=element_blank(),
        legend.position = c(0.3, 0.9),legend.key.size = unit(5, "pt"))



K_original <- vector()
for (i in 1:Length){
  K_original[i] <- K_value(value_of_d[i],u,l)[[3]]
}


K_neglect <- vector()
for (i in 1:Length){
  K_neglect[i] <- K_value(value_of_d[i],U,L)[[3]]
}

K_minmax <- vector()
for (i in 1:Length){
  K_minmax[i] <- K_value(value_of_d[i],u_max,l_min)[[3]]
}

c <- ggplot()+
  geom_line(aes(value_of_d,K_neglect,colour = "Method 1",linetype="Method 1"),size=0.9)+
  geom_line(aes(value_of_d,K_minmax,colour="Method 3",linetype="Method 3"),size=0.8)+
  geom_line(aes(value_of_d,K_original,colour = "Method 2",linetype="Method 2"),size=1.6)+
  labs(title = "Comparison of Theoretical Regret (kd)", x = "The value of d", y = "Theoretical Regret (kd)")+
  #xlim(Sorted_length_2[1], Sorted_length_2[m*N])+
  scale_colour_manual("", values=c("Method 1"="red", "Method 2"="black","Method 3"="blue"))+
  scale_linetype_manual(name = "", values = c("Method 1"=1, "Method 2"=3,"Method 3"=5))+
  theme(legend.title=element_blank(),
        legend.position = c(0.3, 0.9),legend.key.size = unit(5, "pt"))

#install.packages("ggpubr")
library("ggpubr")


library("cowplot")
ggdraw() +
  draw_plot(a, x = 0, y = .5, width = .5, height = .5) +
  draw_plot(b, x = .5, y = .5, width = .5, height = .5) +
  draw_plot(c, x = .25, y = 0, width = .5, height = 0.5) 
  #+draw_plot_label(label = c("A", "B", "C"), size = 15,
                 # x = c(0, 0.5, 0), y = c(1, 1, 0.5))
#ggsave("50_100_1.eps", device = cairo_ps)

```


The comparison of the proportion of bidders' types without queries and the comparison of the confidence rate.


```{r}
number_of_n <- function(d,u,l){
  n <- 0
  for (j in 1:N){
    for (i in 1:m){
      if (u[i,j]-l[i,j]<=d & u[i,j]-l[i,j]>0){
        n <- n+1
      }
      else{
        n <- n+0
      }
    }
  }
  n
}



n_original <- vector()
for (i in 1:Length){
  n_original[i] <- number_of_n(value_of_d[i],u,l)
}

n_neglect <- vector()
for (i in 1:Length){
  n_neglect[i] <- number_of_n(value_of_d[i],U,L)+neglect
}

d <- ggplot()+
  geom_line(aes(value_of_d,n_neglect/(m*N),colour = "Method 1",linetype="Method 1"),size=0.9)+
  geom_line(aes(value_of_d,n_original/(m*N),colour = "Method 2",linetype="Method 2"),size=1.6)+
  labs(title = "Comparison of Type's Proportion Without Query", x = "The value of d", y = "Proportion of type without query")+
  #xlim(Sorted_length_2[1], Sorted_length_2[m*N])+
  scale_colour_manual("", values=c("Method 1"="red", "Method 2"="black"))+
  scale_linetype_manual(name = "", values = c("Method 1"=1, "Method 2"=3))+
  theme(legend.title=element_blank(),
        legend.position = c(0.3, 0.9),legend.key.size = unit(5, "pt"))


e <- ggplot()+
  geom_line(aes(value_of_d,(1-0.01/2)^(n_neglect-neglect),colour = "Method 1",linetype="Method 1"),size=0.9)+
  geom_line(aes(value_of_d,(1-0.01/2)^n_original,colour = "Method 2",linetype="Method 2"),size=1.6)+
  labs(title = "Comparison of Confidence Rate", x = "The value of d", y = "Confidence Rate")+
  #xlim(Sorted_length_2[1], Sorted_length_2[m*N])+
  scale_colour_manual("", values=c("Method 1"="red", "Method 2"="black"))+
  scale_linetype_manual(name = "", values = c("Method 1"=1, "Method 2"=3))+
  theme(legend.title=element_blank(),
           legend.position = c(0.7, 0.9),legend.key.size = unit(5, "pt"))

ggarrange(d, e, 
          labels = c("", ""),
          ncol = 2, nrow = 1)
library("cowplot")


ggdraw() +
  draw_plot(d, x = 0.04, y = 0, width = .4, height = 1) +
  draw_plot(e, x = .55, y = 0, width = .4, height = 1) 
  #+draw_plot_label(label = c("A", "B", "C"), size = 15,
  #+
#ggsave("50_100_2.eps", device = cairo_ps)

```




